\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-20 article.tex
Completed section on set theory

\SubSection{Set theory}

  The characteristics of tags make them excellent for future navigation,
  filtering or search. An object which has been tagged contains a collection,
  or a set, of tags.  Each tag is an element of the set. The order of elements
  within the set is irrelevant, but each element can only occur once.

  For example, $\{1,5,8\}$ denotes a set with three elements: 1, 5 and 8.
  $\{5,8,1\}$ is the same set, since the order of the elements doesn't matter.
  $\{1,1,1\}$, however, is not a valid set because the element 1 occurs
  several times. Elements in a set can also contain strings, so $\{loons,
  penguins, terns\}$ is a valid set.

% set operations

% union, intersection

% Venn diagram
\def\A{A}
\def\B{\V{B}}

%\begin{figure}
\begin{center}
\begin{asy}
size(4cm,0);
pen colour1=red;
pen colour2=green;

picture intersection=new picture;
fill(intersection,c1,colour1+colour2);
clip(intersection,c2);

@@

//draw("$\A$",box,z1);              // Requires [inline] package option.
//draw(Label("$\B$","$B$"),box,z2); // Requires [inline] package option.
draw("$A$",box,z1);            
draw("$\V{B}$",box,z2);

@@

draw(Label("$A\cap B$",0),conj(z)--z0,Arrow,BigMargin);
draw(Label("$A\cup B$",0),z--z0,Arrow,BigMargin);
draw(z--z1,Arrow,Margin(0,m));
draw(z--z2,Arrow,Margin(0,m));

shipout(bbox(0.25cm));
\end{asy}
%\caption{Venn diagram}\label{venn}
\end{center}
%\end{figure}

@@

    \bibitem{golder:ct}
      Scott A. Golder, Bernardo A. Huberman,
      \emph{The Structure of Collaborative Tagging Systems}, 2005.
      \url{http://www.hpl.hp.com/research/scl/papers/tags/tags.pdf}

    \bibitem{heymann:ccch}
      Paul Heymann, Hector Garcia-Molina,
      \emph{Collaborative Creation of Communal Hierarchical Taxonomies in
      Social Tagging Systems}, 2006.
      \url{http://ilpubs.stanford.edu:8090/775/1/2006-10.pdf}

    \bibitem{huang:tt}
      Jeff Huang, Katherine M. Thornton, Efthimis N. Efthimiadis,
      ``Conversational Tagging in Twitter,''
      \emph{Hypertext}, pp. 173-177, 2010.

    \bibitem{jones:folders}
      William Jones, Ammy J. Phuwanartnurak, Rajdeep Gill, Harry Bruce,
      \emph{Don't Take My Folders Away! Organizing Personal Information to Get
      Things Done}, 2005.
      \url{https://dlib.lib.washington.edu/dspace/bitstream/handle/1773/2031/
           Don%27t%20take%20my%20folders%20away%2c%20current.pdf?sequence=2}

    \bibitem{mathes:folk}
      Adam Mathes,
      ``Folksonomies -- Cooperative Classification and Communication Through
      Shared Metadata,''
      \emph{Computer Mediated Communication, LIS590CMC}, 2004.

    \bibitem{shirky:ontology}
      Clay Shirky,
      \emph{Ontology is Overrated: Categories, Links, and Tags}, 2005.
      \url{http://www.shirky.com/writings/ontology_overrated.html}

    \bibitem{wikipedia:tags}
      \emph{Tag (metadata)}, July 12, 2010. \\
      \url{http://en.wikipedia.org/wiki/Tag}

>>>>

\SubSection{Set theory}
  A \emph{set} is a collection of distinct objects. It is a plurality thought
  of as a unit\cite{hausdorff:sets}. \emph{Set theory} is the branch of
  mathematics that studies sets\cite{wikipedia:tags}.

  An object which has been tagged contains a collection, or a set, of tags.
  Each tag is an element of the set. The order of elements within the set is
  irrelevant, but each element can only occur once.

  For example, $\{1,5,8\}$ is a set with three elements: 1, 5 and 8.
  $\{5,8,1\}$ is the same set, since the order of the elements doesn't matter.
  $\{1,1,1\}$, however, is not a valid set because the element 1 occurs
  repeatedly. Elements in a set can contain strings as well, so $\{loons,
  terns, penguins\}$ is also a valid set.

  We usually denote a set by a capital letter for reference purposes. For
  instance, $S=\{1,5,8\}$.

  $a \in S$ denotes that the object $a$ is a member of the set $S$. If $a$
  is not a member of S, we write $a \not \in S$.

  The \emph{union} of two sets $S$ and $T$ is the set

  \[
    S \cup T = \{x:x \in S \: or \: x \in T\}
  \]

% Venn diagram, showing the union of two sets
\def\S{S}
\def\T{\V{T}}

\begin{center}
\begin{asy}
size(4cm,0);
pen colour1=red;
pen colour2=green;

pair z0=(0,0);
pair z1=(-1,0);
pair z2=(1,0);
real r=1.5;
path c1=circle(z1,r);
path c2=circle(z2,r);
fill(c1,colour1);
fill(c2,colour1);

picture intersection=new picture;
fill(intersection,c1,colour1);
clip(intersection,c2,colour1);

@@

draw("$S$",box,z1);            
draw("$\V{T}$",box,z2);

@@

draw(Label("$S\cup T$",0),z--z0,Arrow,BigMargin);
draw(z--z1,Arrow,Margin(0,m));
draw(z--z2,Arrow,Margin(0,m));

shipout(bbox(0.25cm));
\end{asy}
\end{center}

  This consists of those objects which lie in the set $S$ or in the set $T$,
  or in both. So,

  \[
    \{1, 2, 3\} \cup \{3, 4, 5\} = \{1, 2, 3, 4, 5\}
  \]

  The \emph{intersection} of two sets $S$ and $T$ is the set

  \[
    S \cap T = \{x:x \in S \: and \: x \in T\}
  \]

% Venn diagram, showing the intersect of two sets
\def\S{S}
\def\T{\V{T}}

\begin{center}
\begin{asy}
size(4cm,0);
pen colour1=red;
pen colour2=white;

pair z0=(0,0);
pair z1=(-1,0);
pair z2=(1,0);
real r=1.5;
path c1=circle(z1,r);
path c2=circle(z2,r);
fill(c1,colour2);
fill(c2,colour2);

picture intersection=new picture;
fill(intersection,c1,colour1);
clip(intersection,c2);

draw("$S$",box,z1);            
draw("$\V{T}$",box,z2);

draw(Label("$S\cap T$",0),z--z0,Arrow,BigMargin);

shipout(bbox(0.25cm));
\end{asy}
\end{center}

  This consists of those objects which lie in both the set $S$ and the set
  $B$. So,

  \[
    \{1, 2, 3\} \cap \{2, 3, 4\} = \{2, 3\}
  \]

  The \emph{complement} of a set $T$ relative to a set $S$ is the set

  \[
    S - T = \{x:x \in S \: and \: x \not \in T\}
  \]

% Venn diagram, showing the complement of two sets
\def\S{S}
\def\T{\V{T}}

\begin{center}
\begin{asy}
size(4cm,0);
pen colour1=red;
pen colour2=white;

picture intersection=new picture;
fill(intersection,c1,colour2);
clip(intersection,c2);

draw("$S$",box,z1);            
draw("$\V{T}$",box,z2);

draw(Label("$S - T$",0),z--z0,Arrow,BigMargin);
draw(z--z1,Arrow,Margin(0,m));
draw(z--z2,Arrow,Margin(0,m));

shipout(bbox(0.25cm));
\end{asy}
\end{center}

  This consists of those objects which lie in the set $S$ but not in the set
  $T$. So,

  \[
    \{1, 2, 3\} - \{2, 3, 4\} = \{1\}
  \]

  The \emph{symmetric difference} of the sets $S$ and $T$ is the set

  \[
    S \Delta T = \{x:(x \in S \: and \: x \not \in T) \: or \: (x \in T \: and
    \: x \not \in S)\}
  \]

% Venn diagram, showing the symmetric difference of two sets
\def\S{S}
\def\T{\V{T}}

\begin{center}
\begin{asy}
size(4cm,0);
pen colour1=red;
pen colour2=green;
pen colour3=white;

pair z0=(0,0);
pair z1=(-1,0);
pair z2=(1,0);
real r=1.5;
path c1=circle(z1,r);
path c2=circle(z2,r);
fill(c1,colour1);
fill(c2,colour1);

picture intersection=new picture;
fill(intersection,c1,colour3);
clip(intersection,c2);

draw("$S$",box,z1);            
draw("$\V{T}$",box,z2);

draw(Label("$S\cap T$",0),z--z0,Arrow,BigMargin);

shipout(bbox(0.25cm));
\end{asy}
\end{center}

  This consists of those objects which lie either in one of the sets, but not
  in both. So,

  \[
    \{1, 2, 3\} - \{2, 3, 4\} = \{1, 4\}
  \]

% why does this matter? how is it applied to tags and tagging?

@@

    \bibitem{golder:ct}
      S. A. Golder, B. A. Huberman,
      \emph{The Structure of Collaborative Tagging Systems}, 2005.
      \url{http://www.hpl.hp.com/research/scl/papers/tags/tags.pdf}

    \bibitem{heymann:ccch}
      P. Heymann, H. Garcia-Molina,
      \emph{Collaborative Creation of Communal Hierarchical Taxonomies in
      Social Tagging Systems}, 2006.
      \url{http://ilpubs.stanford.edu:8090/775/1/2006-10.pdf}

    \bibitem{hausdorff:sets}
      F. Hausdorff,
      \emph{Set theory},
      Chelsea Publishing Company, 1991.

    \bibitem{huang:tt}
      J. Huang, K. M. Thornton, E. N. Efthimiadis,
      ``Conversational Tagging in Twitter,''
      \emph{Hypertext}, pp. 173-177, 2010.

    \bibitem{jones:folders}
      W. Jones, A. J. Phuwanartnurak, R. Gill, H. Bruce,
      \emph{Don't Take My Folders Away! Organizing Personal Information to Get
      Things Done}, 2005.
      \url{https://dlib.lib.washington.edu/dspace/bitstream/handle/1773/2031/
           Don%27t%20take%20my%20folders%20away%2c%20current.pdf?sequence=2}

    \bibitem{mathes:folk}
      A. Mathes,
      ``Folksonomies -- Cooperative Classification and Communication Through
      Shared Metadata,''
      \emph{Computer Mediated Communication, LIS590CMC}, 2004.

    \bibitem{shirky:ontology}
      C. Shirky,
      \emph{Ontology is Overrated: Categories, Links, and Tags}, 2005.
      \url{http://www.shirky.com/writings/ontology_overrated.html}

    \bibitem{wikipedia:sets}
      \emph{Set theory}, July 19, 2010. \\
      \url{http://en.wikipedia.org/wiki/Set_theory}

    \bibitem{wikipedia:tags}
      \emph{Tag (metadata)}, July 19, 2010. \\
      \url{http://en.wikipedia.org/wiki/Tag}
